### 2025-06-10 index.qmd
20250609 - copyediting

The GitHub repository for the book is located here:\index{GitHub} <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>.
If you have data or analysis examples that are you willing to share and include in the book, feel free to contact me.

@@

Through my training, I have learned the value of statistics for answering important questions that I find interesting.
In graduate training, I came to the realization that statistics are relevant not only for psychology and science, but also for domains that I enjoy as hobbies, including sports and fantasy sports.
I have played in a longstanding fantasy football league for over 20 years (since my junior year of high school) with old friends from high school.
I wanted to apply what I was learning about statistics to help others improve their performance in fantasy football and to help people—including those who might not otherwise be interested—to learn statistics.
So I began blogging online about the value of applying statistics to improve decision making in fantasy football.
Apparently, many people were interested in learning statistics when they could apply them to a domain that they find interesting like fantasy football.
My blog eventually became [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), a website that uses advanced statistics to help people win their fantasy football leagues.

@@

This book was supported by an OpenHawks Open Educational Resources grants program from the University of Iowa Libraries.

>>>>

The GitHub repository for the book is located here:\index{GitHub} <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>.
If you have data or analysis examples that are you are willing to share and include in the book, feel free to contact me.

@@

Through my training, I have learned the value of statistics for answering important questions that I find interesting.
In graduate training, I came to the realization that statistics is relevant not only for psychology and science, but also for domains that I enjoy as hobbies, including sports and fantasy sports.
I have played in a longstanding fantasy football league for over 20 years (since my junior year of high school) with old friends from high school.
I wanted to apply what I was learning about statistics to help others improve their performance in fantasy football and to help people—including those who might not otherwise be interested—to learn statistics.
So I began blogging online about the value of applying statistics to improve decision making in fantasy football.
Apparently, many people were interested in learning statistics when they could apply them to a domain that they find interesting, like fantasy football.
My blog eventually became [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), a website that uses advanced statistics to help people win their fantasy football leagues.

@@

This book was supported by an OpenHawks Open Educational Resources grant program from the University of Iowa Libraries.
